A sheaf--function dictionary for algebraic tori over local fields

### 2013-08-17 shanghai.tex
Biblio style updates
More improvements to Greenberg of Neron.

@@

See \cite{greenberg:63a} and \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6}
and the first few sections of \cite{stasinski:12a} for background on the Greenberg functor.

>>>>

We will also need the Greenberg functor, 
introduced in \cite{greenberg:61} and \cite{greenberg:63a}, 
as functor from the category of schemes locally of finite type 
over an Artinian local ring $A$ with perfect residue field $k$ 
to the category of schemes locally of finite type over $k$. 
This functor enjoys many pleasing properties: 
it respects open immersions, closed immersions, 
etale morphisms and smooth morphisms. 
Besides Greenberg's original papers, 
see \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6} 
and the first few sections of \cite{stasinski:12a} 
for background on the Greenberg functor. 
Let
\[
%\begin{tikzcd}
\Gr_d : \left( \text{Schemes} \atop \text{lft over $\OK$}\right) \to \left( \text{Schemes} \atop \text{lft over $\OK$}\right)
%\end{tikzcd}
\]
be the functor produced by precomposing pull-back along $\OK \to \OK/\pK^d$ with the Greenberg functor.

@@
